SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-06-11 scipy-1.0/subpackages.tex
Pruned end material
removed reference to SI

    This subpackage includes the following, with additional details in the SI:
    simplex and interior-point linear programming solvers,
		implementations of many nonlinear minimization algorithms,  

>>>>

		This subpackage includes simplex and interior-point linear programming
		solvers, implementations of many nonlinear minimization algorithms,
